### 2019-12-09 progress_update/figs/recursive/fig.tex

  \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};

  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};

  \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};

  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net) edge (time_t_1);

  \node[text width=1cm,align=center] (x_y) at (time_t.center) {Input\\ channels};
  \node[text width=1cm,align=center] (x_y_1) at (time_t_1.center) {Otput\\ channels};

  \node[roundnode] (number) at (0, -2.3) {$3.14$};

  \node[draw, circle] (quest) at (2, -0.6) {\textbf{\large ?}};
  \draw [->,line width=1pt, shorten >=3pt, shorten <=4pt] (number.east) -- (2,-2.3) -- (2,-1);

>>>>

  \draw [dashed, draw=blue!80, fill=blue!4, opacity=1] (-2, 1.5) rectangle (1.7, -1.3);

  \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};
  \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};
  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net) edge (time_t_1);

  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_1) at (4,-3) {Network};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_t_1.south) -- (8, -1.5) -- (0, -1.5) -- (0, -3) -- (net_1.west);
  \node[cascaded,label=below:Time $t+2$] (time_1_t_1) at (8,-3) {};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_1) edge (time_1_t_1);

  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_2) at (4,-6) {Network};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_1_t_1.south) -- (8, -4.5) -- (0, -4.5) -- (0, -6) -- (net_2.west);
  \node[cascaded,label=below:Time $t+3$] (time_2_t_1) at (8,-6) {};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_2) edge (time_2_t_1);

### 2019-12-09 progress_update/figs/simple_eval/fig.tex

  \draw [dashed, draw=blue!80, fill=blue!4, opacity=1] (-2, 1.5) rectangle (1.7, -1.3);

  \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};
  \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};
  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net) edge (time_t_1);

  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_1) at (4,-3) {Network};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_t_1.south) -- (8, -1.5) -- (0, -1.5) -- (0, -3) -- (net_1.west);
  \node[cascaded,label=below:Time $t+2$] (time_1_t_1) at (8,-3) {};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_1) edge (time_1_t_1);

  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_2) at (4,-6) {Network};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (time_1_t_1.south) -- (8, -4.5) -- (0, -4.5) -- (0, -6) -- (net_2.west);
  \node[cascaded,label=below:Time $t+3$] (time_2_t_1) at (8,-6) {};
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_2) edge (time_2_t_1);

>>>>

  \draw [dashed, draw=blue!80, fill=blue!4, opacity=1] (-2, 1.5) rectangle (1.7, -7.6);

  \node[cascaded,label=below:Time $t$] (time_t) at (0,0) {};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net) at (4,0) {Network};
  \node[cascaded,label=below:Time $t+1$] (time_t_1) at (8,0) {};

  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_t) edge (net);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net) edge (time_t_1);

  \node[cascaded,label=below:Time $t$] (time_1_t) at (0,-3) {};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_1) at (4,-3) {Network};
  \node[cascaded,label=below:Time $t+1$] (time_1_t_1) at (8,-3) {};
  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_1_t) edge (net_1);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_1) edge (time_1_t_1);

  \node[cascaded,label=below:Time $t$] (time_2_t) at (0,-6) {};
  \node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em] (net_2) at (4,-6) {Network};
  \node[cascaded,label=below:Time $t+1$] (time_2_t_1) at (8,-6) {};
  \draw [->,line width=1pt, shorten >=3pt, shorten <=9pt] (time_2_t) edge (net_2);
  \draw [->,line width=1pt, shorten >=10pt, shorten <=3pt] (net_2) edge (time_2_t_1);
